---
title: Accuracy in returning sampled coefficient
author: "Amelia"
date: "19/10/2019"
output:
  html_document: default
  pdf_document: default
---
This document takes as inputs the final_master_df files created by calc_coeff_diffs_glm_brms.R

```{r read in data, warnings = FALSE, message = FALSE,echo=FALSE}

#number of subjects depends on isntance and is hard coded 

# full compelement- correct and incorrect models 
hindi_dinst7<-readr::read_csv("final_master_hindi_dinst7.csv") # coef 10, -10, 0
  hindi_dinst7$experiment<- "old_hindi_design"

three_each<-readr::read_csv("final_master_3each_dups_dinst1_30subjs.csv") 
  three_each$experiment<- "3_each_dups"
  three_each$m_stanfile <- as.character(three_each$m_stanfile)
  
four_each<-readr::read_csv("final_master_4each_dups_dinst1_30subjs.csv") 
  four_each$experiment<- "4_each_dups"
  four_each$m_stanfile <- as.character(four_each$m_stanfile)


hindi_for_hists_full<-dplyr::bind_rows(hindi_dinst7,
                                       three_each,
                                       four_each)

hindi_for_hists <-dplyr::filter(hindi_for_hists_full,is_correct_model==TRUE)


  

```

## for the subset of correct models

```{r glm diffs, echo=FALSE}

ggplot2::ggplot(hindi_for_hists, ggplot2::aes(x = Econ_glm_diff)) +
    ggplot2::geom_histogram(binwidth = .1,
                            position="identity",
                            alpha = 0.4)+
    ggplot2::scale_x_continuous(limits = c(-10,10))+
    ggplot2::ggtitle("Econ coef differenece,hindi data,
                                        calculated by glm, by number of subjects")+
    ggplot2::facet_grid(experiment ~ .)


ggplot2::ggplot(hindi_for_hists, ggplot2::aes(x = Glob_glm_diff)) +
    ggplot2::geom_histogram(binwidth = .1,
                            position="identity",
                            alpha = 0.4)+
    ggplot2::scale_x_continuous(limits = c(-10,10))+
    ggplot2::ggtitle("Glob coef differenece, hindi data,
                     calculated by glm, by number of subjects")+
    ggplot2::facet_grid(experiment ~ .)


ggplot2::ggplot(hindi_for_hists, ggplot2::aes(x = Loc_glm_diff)) +
    ggplot2::geom_histogram(binwidth = .1,
                            position="identity",
                            alpha = 0.4)+
    ggplot2::scale_x_continuous(limits = c(-10,10))+
    ggplot2::ggtitle("Loc coef differenece, hindi data,
                                 calculated by glm, by number of subjects")+
    ggplot2::facet_grid(experiment ~ .)




```

## New 3 each design (three pairs per hindi phone, 216 trials) 

### (returned model coef)-(input sampling coef) Faceted by whether a correct or incorrect model is applied, brms mods

```{r glm diffs full mods, echo=FALSE}

ggplot2::ggplot(three_each, ggplot2::aes(x = Econ_brms_diff)) +
    ggplot2::geom_histogram(binwidth = .1,
                            position="identity",
                            alpha = 0.4)+
    ggplot2::scale_x_continuous(limits = c(-7.5,7.5))+
    ggplot2::ggtitle("Econ coef differenece,hindi data,
                                        calculated by brms,")+
    ggplot2::facet_grid(is_correct_model ~ .)


ggplot2::ggplot(three_each, ggplot2::aes(x = Glob_brms_diff)) +
    ggplot2::geom_histogram(binwidth = .1,
                            position="identity",
                            alpha = 0.4)+
    ggplot2::scale_x_continuous(limits = c(-7.5,7.5))+
    ggplot2::ggtitle("Glob coef differenece, hindi data,
                     calculated by brms")+
    ggplot2::facet_grid(is_correct_model ~ .)


ggplot2::ggplot(three_each, ggplot2::aes(x = Loc_brms_diff)) +
    ggplot2::geom_histogram(binwidth = .1,
                            position="identity",
                            alpha = 0.4)+
    ggplot2::scale_x_continuous(limits = c(-7.5,7.5))+
    ggplot2::ggtitle("Loc coef differenece, hindi data,
                                 calculated by brms")+
    ggplot2::facet_grid(is_correct_model ~ .)


```

## New 4 each design (four pairs per hindi phone, 144 trials) 

### (returned model coef)-(input sampling coef) Faceted by whether a correct or incorrect model is applied, glm mods 
```{r brms diffs full mods, echo=FALSE}

ggplot2::ggplot(four_each, ggplot2::aes(x = Econ_brms_diff)) +
    ggplot2::geom_histogram(binwidth = .1,
                            position="identity",
                            alpha = 0.4)+
    ggplot2::scale_x_continuous(limits = c(-7.5,7.5))+
    ggplot2::ggtitle("Econ coef differenece,hindi data,
                                        calculated by brms,")+
    ggplot2::facet_grid(is_correct_model ~ .)


ggplot2::ggplot(four_each, ggplot2::aes(x = Glob_brms_diff)) +
    ggplot2::geom_histogram(binwidth = .1,
                            position="identity",
                            alpha = 0.4)+
    ggplot2::scale_x_continuous(limits = c(-7.5,7.5))+
    ggplot2::ggtitle("Glob coef differenece, hindi data,
                     calculated by brms")+
    ggplot2::facet_grid(is_correct_model ~ .)


ggplot2::ggplot(four_each, ggplot2::aes(x = Loc_brms_diff)) +
    ggplot2::geom_histogram(binwidth = .1,
                            position="identity",
                            alpha = 0.4)+
    ggplot2::scale_x_continuous(limits = c(-7.5,7.5))+
    ggplot2::ggtitle("Loc coef differenece, hindi data,
                                 calculated by brms")+
    ggplot2::facet_grid(is_correct_model ~ .)


```

